Thermodynamic fragments for magic states in quantum computation

### 2021-02-24 appendix.tex
Tidied up before the mana section

\subsection{Mana properties}
Mana monotonicity in any $\sigma$--fragment can be directly seen due to statement~\ref{en:tm3} in~\cref{thm:dmajor} for $t=0$.
Furthermore, mana is additive due to the multiplicative property~\ref{en:w4} of~\cref{thm:wstate}.

@@

\begin{theorem}\label{thm:frag}
    Let $\R = (\O, \F)$ be a magic theory. 
    The following statements hold:
    \begin{enumerate}
        \item No $\sigma$-fragment is empty.
        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
        \begin{equation}
            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
        \end{equation}
        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
    \end{enumerate}
\end{theorem}
\begin{proof}$ $\\

@@

@@

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\ell\in [1,nf-1]$,
	\begin{align}
		&\left[ 8\ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)} \leq \binom{nf}{\ell} \leq \\
		&\left[ 2\pi \ell\left(1-\frac{\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{nf S\left(\frac{\ell}{nf}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\ell = 1,2, nf-1, nf-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(af; nf, p) \geq \sum\limits_{\ell=0}^{af/2}\left[ 16\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
		&\text{2. } \Phi_+(af; nf, p) \leq \sum\limits_{\ell=0}^{af/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-nf\ent{\frac{2\ell}{nf}}{p}}, \\
		&\hspace{14pt} \text{for all even } af\in [2,nf] \\
		&\text{3. } \Phi_-(af; nf, p) \geq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd }af\in [1,nf] \\
		&\text{4. } \Phi_-(af; nf, p) \leq \sum\limits_{\ell=1}^{(af-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-nf\ent{\frac{2\ell+1}{nf}}{p}},\ \text{for all odd } af\in [1,nf]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

\ddd{Note the following is relevant: you might have $W_{\bmq} = W_{\bmq'}$ for two different $\bmq$, $\bmq'$. This would make a difference to our calculations for the first elbow. Check this doesn't occur. (If it does, our analysis is still correct, but it simply could be improved).}
\nick{It can occur accidentally, but it doesn't make a difference for first elbow analysis, as we ``bring the top Lorenz curve down till its first elbow touches the bottom Lorenz curve''. Basically, Lorenz curves have fewer elbows, but because the first elbow constraint boils down to a ratio comparison~\cref{eq:first_elb_bound} it doesn't change the analysis.}
\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}

\begin{theorem}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$-fragment.

	Let $n'$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ and $E \coloneqq \{x_1, \dots, x_n'\}$ be their locations.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,n'$.
\end{theorem}
\begin{proof}	
	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.

>>>>

\begin{proposition}\label{thm:lccont}
	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$.
\end{proposition}
\begin{proof}
	If $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
\end{proof}

@@

\begin{theorem}\label{thm:frag_app}
    Let $\R = (\O, \F)$ be a magic theory. 
    The following statements hold:
    \begin{enumerate}
        \item No $\sigma$-fragment is empty.
        \item If a free operation leaves two states invariant, then it also leaves their mixtures invariant, 
        \begin{equation}
            \O_{\sigma} \cap \O_{\sigma'} \subseteq \O_{p\sigma + (1-p)\sigma'}\ \text{for all}\ p \in [0,1].
        \end{equation}
        \item Let $\E$ be a $\cptp$ operation with Wigner distribution $\W{\E}$.
        For $\R = \Rmax$ $\E \in \O_\sigma$ iff $\W{\E} \in \stochw$.
    \end{enumerate}
\end{theorem}
\begin{proof}$ $\\

@@

Single-copy Lorenz curves are simply additive in noise, 
\begin{equation}
\lc{(1-\epsilon)\rho + \epsilon\sigma}{\sigma} = (1-\epsilon)\lc{\rho}{\sigma} + \epsilon\lc{\sigma}{\sigma},
\end{equation}
for any $\sigma, \rho$.
This is not true for higher number of copies.

@@

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\ell\in [1,np-1]$,
	\begin{align}
		&\left[ 8\ell\left(1-\frac{\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{np}\right)} \leq \binom{np}{\ell} \leq \\
		&\left[ 2\pi \ell\left(1-\frac{\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{n S\left(\frac{\ell}{np}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\ell = 1,2, np-1, np-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(a; n, p) \geq \sum\limits_{\ell=0}^{np/2}\left[ 16\ell\left(1-\frac{2\ell}{np}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{nf}}{p}}, \\
		&\hspace{14pt} \text{for all even } a\in [2,np] \\
		&\text{2. } \Phi_+(a; n, p) \leq \sum\limits_{\ell=0}^{np/2}\left[ 4\pi\ell\left(1-\frac{2\ell}{nf}\right) \right]^{-\frac{1}{2}} 2^{-n\ent{\frac{2\ell}{np}}{p}}, \\
		&\hspace{14pt} \text{for all even } a\in [2,np] \\
		&\text{3. } \Phi_-(a; n, p) \geq \sum\limits_{\ell=1}^{(np-1)/2}\left[ 16(\ell+1)\left(1-\frac{2\ell+1}{np}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{np}}{p}},\ \text{for all odd }a\in [1,np] \\
		&\text{4. } \Phi_-(a; n, p) \leq \sum\limits_{\ell=1}^{(np-1)/2}\left[ 4\pi(\ell+1)\left(1-\frac{2\ell+1}{nf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-n\ent{\frac{2\ell+1}{np}}{p}},\ \text{for all odd } a\in [1,np]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

\subsection{Lorenz curve independent constraints}\label{app:lc_constraints}

\begin{theorem}\label{thm:elbows}
	Let $\rho, \tau$ be two quantum states with Lorenz curves $\lc{\rho}{\sigma}(x), \lc{\tau}{\sigma}(x)$ in the $\sigma$--fragment.

	Let $t$ be the number of elbows of $\lc{\tau}{\sigma}(x)$ at locations $x_1, \dots, x_t$.

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i =1,\dots,t$.
\end{theorem}
\begin{proof}	
	$\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ trivially implies $\lc{\rho}{\sigma}(x_{i}) \geq \lc{\tau}{\sigma}(x_{i})$ for all $i = 1,\dots,n'$.
